Ms 1

### 2017-11-22 ms1/ms1_display.Rmd
minor

claims_by_abx %>%
  filter(abx %in% c('overall', 'overall_approp', 'overall_inapprop')) %>%
  ggplot(aes(x=year, y=cpkp, color=abx)) +
  geom_point() + geom_line() +
  #scale_y_continuous(limits=c(0, 1525), breaks=c(1000, 1125, 1250, 1375, 1500)) +
  scale_y_continuous(limits=c(0, 1525), breaks=c(0, 250, 500, 750, 1000, 1250, 1500)) +
  theme_minimal() +
  ggtitle('Unadjusted consumption, all abx')

claims_by_abx %>%
  filter(abx %in% c('azithromycin', 'ciprofloxacin', 'amoxicillin', 'cephalexin', 'tmpsmx', 'levofloxacin')) %>%
  ggplot(aes(x=year, y=cpkp, color=abx)) +
  geom_point() + geom_line() +
  scale_y_continuous(limits=c(0, 250), breaks=c(0, 50, 100, 150, 200, 250)) +
  theme_minimal() +
  ggtitle('Unadjusted consumption, top 5')

claims_by_abx %>%
  filter(abx %in% c('amoxclav', 'doxycycline', 'nitrofurantoin', 'clindamycin')) %>%
  ggplot(aes(x=year, y=cpkp, color=abx)) +
  geom_point() + geom_line() +
  scale_y_continuous(limits=c(0, 100), breaks=c(0, 50, 100)) +
  theme_minimal() +
  ggtitle('Unadjusted consumption, next 5')
```

@@

@@

combined_table = dx_to_pde_table %>%
  mutate(f_with_abx=format_pct(f_with_abx)) %>%
  spread(year, f_with_abx) %>%
  left_join(dx_to_pde_trends, by=c('dx_cat', 'abx')) %>%
  mutate(p.value=format_p(p.value)) %>%
  arrange(abx, dx_cat)
```

@@

trends_by_demography = read_tsv('tables/demography_models.tsv') %>%
  filter(term=='year') %>%
  mutate(estimate=3*estimate,
         std.error=sqrt(3)*std.error) %>%
  mutate(ci=1.96*std.error,
         ci_lo=estimate-ci,
         ci_hi=estimate+ci) %>%
  mutate(y=est2pct(estimate),
         ymin=est2pct(ci_lo),
         ymax=est2pct(ci_hi)) %>%
  mutate(change=sprintf('%.2f (%.2f -- %.2f)', y, ymin, ymax)) %>%
  select(group_type, group, change)

>>>>

claims_by_abx %>%
  filter(abx %in% c('overall', 'overall_approp', 'overall_inapprop')) %>%
  ggplot(aes(x=year, y=cpkp, color=abx)) +
  geom_line() +
  scale_y_continuous(limits=c(0, 1400), breaks=c(0, 250, 500, 750, 1000, 1250, 1400)) +
  coord_fixed(ratio=4/1400*1.25) +
  theme_minimal() +
  theme(panel.grid.minor.x=element_blank()) +
  ggtitle('Unadjusted consumption, all abx')

claims_by_abx %>%
  filter(abx %in% c('azithromycin', 'ciprofloxacin', 'amoxicillin', 'cephalexin', 'tmpsmx', 'levofloxacin')) %>%
  ggplot(aes(x=year, y=cpkp, color=abx)) +
  geom_line() +
  scale_y_continuous(limits=c(0, 250), breaks=c(0, 50, 100, 150, 200, 250)) +
  coord_fixed(ratio=4/250*1.25) +
  theme_minimal() +
  theme(panel.grid.minor.x=element_blank()) +
  ggtitle('Unadjusted consumption, top 5')

claims_by_abx %>%
  filter(abx %in% c('amoxclav', 'doxycycline', 'nitrofurantoin', 'clindamycin')) %>%
  ggplot(aes(x=year, y=cpkp, color=abx)) +
  geom_line() +
  scale_y_continuous(limits=c(0, 100), breaks=c(0, 50, 100)) +
  coord_fixed(ratio=4/100*1.25) +
  theme_minimal() +
  theme(panel.grid.minor.x=element_blank()) +
  ggtitle('Unadjusted consumption, next 5')
```

@@

## Raw inappropriate fractions

```{r inappropriate_fraction}
claims_by_abx %>%
  spread(abx, cpkp) %>%
  mutate(pct_inapprop = overall_inapprop / overall * 100) %>%
  select(year, pct_inapprop) %>%
  kable(caption='Raw fraction of inappropriate prescribing')
```

@@

combined_table = dx_to_pde_table %>%
  mutate(f_with_abx=format_pct(f_with_abx)) %>%
  spread(year, f_with_abx) %>%
  left_join(dx_to_pde_trends, by=c('dx_cat', 'abx')) %>%
  mutate(p.value=format_p(p.value)) %>%
  arrange(dx_cat, abx)
```

@@

trends_by_demography = read_tsv('tables/demography_models.tsv') %>%
  filter(term=='year') %>%
  mutate(estimate=3*estimate,
         std.error=sqrt(3)*std.error) %>%
  mutate(ci=1.96*std.error,
         ci_lo=estimate-ci,
         ci_hi=estimate+ci) %>%
  mutate(y=est2pct(estimate),
         ymin=est2pct(ci_lo),
         ymax=est2pct(ci_hi)) %>%
  mutate(change=sprintf('%.2f (%.2f -- %.2f)', y, ymin, ymax)) %>%
  select(group_type, group, change, p.value)
